Information Aggregation in Exponential Family Markets

### 2014-02-12 WriteUp/maxentpredmkts.tex
tiny edit

Notice that Lemma~\ref{thm:growth} only required that the market state to which the trader moves be representable as a convex combination of the current market state and his belief. This means that the result holds for exponential utility traders aiming to maximize their utility by Theorem~\ref{thm:exp-util}. In this case, the trader who moves the market state can expect his profit to be positive and at least $\frac{1}{a}D_{T}(\theta,\htheta)$ where $a$ is the exponential utility parameter. When the cost function is adjusted to $C_{\lambda}$ with an inverse liquidity parameter $\lambda$ Section \ref{sec:exputil},  the trader receives an expected payoff of at least $\frac{1}{a} D_{T}(\lambda\theta,\htheta)$.

>>>>

Notice that Lemma~\ref{thm:growth} only required that the market state to which the trader moves be representable as a convex combination of the current market state and his belief. This means that the result holds for exponential utility traders aiming to maximize their utility by Theorem~\ref{thm:exp-util}. In this case, the trader who moves the market state can expect his profit to be positive and at least $\frac{1}{a}D_{T}(\theta,\htheta)$ where $a$ is the exponential utility parameter. When the cost function is adjusted to $C_{\lambda}$ with an inverse liquidity parameter $\lambda$ as in Section \ref{sec:exputil},  the trader receives an expected payoff of at least $\frac{1}{a} D_{T}(\lambda\theta,\htheta)$.
